Kung Faux Pandas \\ \large Alternative Facts for Privacy Protection

### 2018-05-30 paper/main.tex
Auto Update from local Sharelatex

\author{
  James King \& Seth Russell\\
  Data Science to Patient Value (D2V)\\
  School of Medicine \\
  University of Colorado Anschutz Medical Campus\\
  Aurora, CO\\
  \texttt{james.king@ucdenver.edu} \\
  \texttt{seth.russell@ucdenver.edu} \\
  }

@@

\begin{chapquote}{Richard Dawkins on his preference for the scientific method over other modes of inquiry.}
``Because it works, bitches.''
\end{chapquote}

@@

In the United States, there's been a long-standing regulation described in the Health Insurance Portability and Accountability Act (HIPAA), which mandates strong security on data related to health care and is backed by significant fines and possible criminal charges \cite{hippaviol}.  Thus, even institutitions which which to share data face a steep institutional risk.   This makes it virtually impossible to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.

Perhaps more ominously for researchers, on \hl{May 25 , 2018}, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{<get the text of the rules cited>}, establishing a new paradigm in data ``ownership'' for that jurisdiction.   In short, this set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing  that data to  honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.

@@

\section{Methods}

@@

>>>>

\author{
  James King, Seth Russell, Tellen D. Bennett, Debashis Ghosh\\
  Data Science to Patient Value (D2V)\\
  School of Medicine \\
  University of Colorado Anschutz Medical Campus\\
  Aurora, CO\\
  \texttt{james.king@ucdenver.edu}, \texttt{seth.russell@ucdenver.edu},\\ \texttt{tell.bennett@ucdenver.edu} \texttt{debashis.ghosh@ucdenver.edu}
  }

@@

@@

In the United States, there's been a long-standing regulation described in the Health Insurance Portability and Accountability Act (HIPAA), which mandates strong security on data related to health care and is backed by significant fines and possible criminal charges \cite{hippaviol}.  Thus, even institutions which share data face a steep institutional risk. This makes it virtually impossible to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.

Perhaps more ominously for researchers, on May 25 , 2018, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{<get the text of the rules cited>}, establishing a new paradigm in data ``ownership'' for that jurisdiction.   In short, this set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing  that data to  honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.

@@

\section{System Details}

@@

\subsection{System Structure}
KFP provides a class
